Through the eyes of the teacher - Multimodal exploration of expertise differences in the perception of classroom disruptions

### 2022-07-07 02_paper/02_study/paper_methods.Rmd
Update paper_methods.Rmd

```{r item_analysis_classroom_management_novice, echo=FALSE, include=FALSE, results='asis'}
quest.data %>%
  dplyr::filter(Group == "Novice") %>% 
  dplyr::select(contains("LM")) %>%
  as.data.frame() %>%
  tab_itemscale(CSS = list(
    css.firsttablerow.col7 = "'cronbachs alpha';"
  ))
```

@@

>>>>

```
XXX FRANZI
```{r item_analysis_classroom_management_novice, echo=FALSE, include=FALSE, results='asis'}
quest.data %>%
  dplyr::filter(Group == "Novice") %>% 
  dplyr::select(contains("LM")) %>%
  as.data.frame() %>%
  tab_itemscale(CSS = list(
    css.firsttablerow.col7 = "'cronbachs alpha';"
  ))
```

@@

```
XXX FRANZI
